%\newpage
%
%
%\bibliographystyle {gost2008s}
%\bibliography {dissbib}
%\printbibliography
% \nocite {*} % добавляет непроцитированные источники из bib-файла


\addcontentsline{toc}{chapter}{Список использованных источников и литературы} % Добавляем раздел в содержание

%\bibliographystyle {gost2008s}
%\bibliography {dissbib}
%\nocite {*}
%\nocite{*}
% \printbibliography[
%                     title = {Список использованных источников и литературы}]

\begin{thebibliography}{99}

\bibitem{SSS7}
{\bf Bandt C., Graf S. }
Self-Similar Sets 7. A Characterization of Self-Similar Fractals with Positive Hausdorff Measure // Proceedings of the American Mathematical Society. 1992. Т. 114. № 4. С. 995–1001.

\bibitem{SSS2}
{\bf Bandt C., Keller K.}
Self‐Similar Sets 2. A Simple Approach to the Topological Structure of Fractals // 
Mathematische Nachrichten. 1991. Т. 154. № 1. С. 27--39.

\bibitem{SSS6}
{\bf Bandt, C., Stahnke, J.}
Self-similar sets 6. Interior distance on deterministic fractals. //
preprint, 1990

\bibitem{Bedford1984}
{\bf Bedford, T. }
Crinkly curves, Markov partitions and dimension: Phd Thesis / University of Warwick, 1984.

\bibitem{Ces}
{\bf Cesaro, E.} 
Remarques sur la courbe de von Koch // 
Atti della R. Accad. della Scienze fisiche e matem. Napoli. 1905. T. 12. № 15. С. 1--12.

\bibitem{Char1998}
{\bf Charatonik J. J., Charatonik W. J.}
Dendrites // 
Aportaciones Mat. Comun. 1998. Т. 22. С. 227--253.

\bibitem{CS1}
{\bf Cristea L. L., Steinsky B. }
Curves of infinite length in $4\times4$-labyrinth fractals// 
Geometriae Dedicata. 2008. Т. 141. № 1. С. 1--17.


\bibitem{CS2}
{\bf Cristea L. L., Steinsky B. }
Curves of infinite length in labyrinth fractals // 
Proceedings of the Edinburgh Mathematical Society. 2011. Т. 54. № 2. С. 329--344.


\bibitem{CS3}
{\bf Cristea L. L., Steinsky B. }
Mixed labyrinth fractals // 
Topology and its Applications. 2017. Т. 229. С. 112--125.

\bibitem{Falconer2004}
{\bf Falconer, K. J.} 
Fractal geometry: mathematical foundations and applications / 
K. J. Falconer. -- 3rd ed. -- New York: J.~Wiley and Sons., 2014. -- 398 p.

\bibitem{Fraser_2021}
{\bf Fraser J. M. }
Fractal Geometry of Bedford-McMullen Carpets // 
Thermodynamic Formalism / под ред. M. Pollicott, S. Vaienti. : Springer International Publishing, 2021. С. 495--516.

\bibitem{Hata1985}
{\bf Hata M. }
On the structure of self-similar sets // 
Japan Journal of Applied Mathematics. 1985. Т. 2. № 2. С. 381–414.

\bibitem{Hut1981}
{\bf Hutchinson J. }
Fractals and Self-Similarity // 
Indiana University Mathematics Journal. 1981. Т. 30. № 5. С. 713–747.

\bibitem{LLR2013}
{\bf Lau K.-S., Luo J. J., Rao H. }
Topological structure of fractal squares // 
Mathematical Proceedings of the Cambridge Philosophical Society. 2013. Т. 155. № 1. С. 73--86.

\bibitem{KenyonPeres1996}
{\bf Kenyon R., Peres Y.,} 
Measures of full dimension on affine-invariant sets // 
Ergodic Theory and Dynamical Systems. 1996. Т. 16. № 2. С. 307–323.

\bibitem{Koch}
{\bf H.~von~Koch},  
Sur une courbe continue sans tangente, obtenue par
une construction geometrique elementaire // 
Archiv for Matemat., Astron. och Fys., 1904, Т.~1, С.~681--702.

\bibitem{Kur1} 
{\bf Kuratowski, K.} 
Topology : vol. 1 / 
K. Kuratowski. -- Academic Press, 1966. -- 580 p.

\bibitem{Kur2} 
{\bf Kuratowski, K.} 
Topology : vol. 2 / 
K. Kuratowski. -- Academic Press, 1968. -- 608 p.

\bibitem{Levy1939}
{\bf L{\'e}vy, P.} 
Les courbes planes ou gauches et les surface compos{\'e}es de parties semblables au tout // 
J. I’Ecole Poly. 1939. Т. 144. С. 227--292.

\bibitem{McMullen1984}
{\bf McMullen C. }
The Hausdorff dimension of general Sierpiński carpets // 
Nagoya Mathematical Journal. 1984. Т. 96. С. 1–9.

\bibitem{McWorter1987}
{\bf McWorter Jr. W. A., Tazelaar J. M.}
Creating fractals // 
Byte. 1987. Т. 12. № 9. С. 123--132.

\bibitem{MW1988}
{\bf Mauldin R. D., Williams S. C.}
Hausdorff dimension in graph directed constructions // 
Transactions of the American Mathematical Society. 1988. Т. 309. № 2. С. 811--829.

\bibitem{Moran1996}
{\bf Moran M.}
Hausdorff measure of infinitely generated self-similar sets // 
Monatshefte für Mathematik. 1996. Т. 122. № 4. С. 387--399.

\bibitem{Moran1946}
{\bf Moran P. A. P. }
Additive functions of intervals and Hausdorff measure // 
Mathematical Proceedings of the Cambridge Philosophical Society. 1946. Т. 42. № 1. С. 15–23.

\bibitem{Peres1994}
{\bf Peres Y.,}
The self-affine carpets of McMullen and Bedford have infinite Hausdorff measure // 
Mathematical Proceedings of the Cambridge Philosophical Society. 1994. Т. 116. № 3. С. 513--526.

\bibitem{STV2017}
{\bf Samuel M., Tetenov A. V., Vaulin D. A. }
Self-similar dendrites generated by polygonal systems in the plane //
Siberian Electronic Mathematical Reports. 2017. Т. 14. С. 737--751.

\bibitem{Schief1994} 
{\bf Schief,~A.}  Separation properties for self-similar sets.// 
Proc. Amer. Math. Soc., 1994, V.112, No.~1, pp.~111--115.

\bibitem{strich1999}
{\bf Strichartz R. S. }
Analysis on fractals // 
Notices AMS. 1999. Т. 46. № 10. С. 1199--1208.

\bibitem{Strichartz1999}
{\bf Strichartz R. }
Isoperimetric Estimates on Sierpinski Gasket Type Fractals // 
Transactions of the American Mathematical Society. 1999. Т. 351. № 5. С. 1705--1752.

\bibitem{FIP}
{\bf Tetenov A. }
Finiteness properties for self-similar continua // 
arXiv:2003.04202v2 [math.MG]. 2021.

\bibitem{Xiao2021}
{\bf Xiao J.-C. }
Fractal squares with finitely many connected components // 
Nonlinearity. 2021. Т. 34. № 4. С. 1817--1836.

\bibitem{Zerner1996} 
{\bf Zerner, M. P. W.} 
Weak separation properties for self-similar sets // 
Proc. Amer. Math. Soc.  -- 1996. -- vol.~124, no.~11. -- pp.~3529--3539.


%
%\bibitem{}
%{\bf }
%
%\bibitem{}
%{\bf }
%
%
%
%\bibitem{}
%{\bf }
%
%
%
%\bibitem{}
%{\bf }
%
%
%
%\bibitem{}
%{\bf }

\bibitem{ATK}  
{\bf Асеев,~В.~В.} 
О самоподобных жордановых кривых на плоскости / 
В.~В.~Асеев, А.~В~Тетенов., А.~С.~Кравченко //
Сиб. мат. журн., 2003, Т. 44, № 3, С.~481 -- 492.

\bibitem{2} 
{\bf Асеев~В.~В.} 
О жордановых самоподобных дугах, допускающих структурную параметризацию /
В.~В.~Асеев, А.~В.~Тетенов //
Сиб. матем. журн. (2005), том 46, № 4, С.~733 -- 748.

\bibitem{VDT} 
{\bf Ваулин Д.А.}
О связных компонетнах фрактальных кубов / 
Д.~А.~Ваулин, Д.~А.~Дроздов, А.~В.~Тетенов //
Труды ИММ УРО РАН, 2020, т.26, № 2, С.~98 -- 107.

\bibitem{TSV2017} 
{\bf Тетенов~А.~В.}  
О дендритах, заданных системами полиэдров и их точках ветвления /
А.~В.~Тетенов, М.~Самуэль, Д.~А.~Ваулин // 
Труды ИММ УРО РАН, 2017, т.23, № 4, С.~281 -- 291.

\bibitem{Tet06}
{\bf Тетенов~А.~В.}
Самоподобные жордановы дуги и граф-ориентированные системы подобий /
А.~В.~Тетенов //
Сиб. мат. журн. 2006. Т. 47, № 5, С.~1147 -– 1159.

\bibitem{Tet07}
{\bf Тетенов А.~В.} 
Структурные теоремы в теории самоподобных фракталов : диссертация на соискание уч. степени доктора физико-математических наук / А.В. Тетенов -- Горно-Алтайск, 2010. -- 216~с. 

\bibitem{Kig}
{\bf Kigami~J.}, 
Analysis on fractals. Cambridge Tracts in Mathematics 143, 
Cambridge University Press, 2001, 233 p.

\bibitem{FPS}
{\bf Tetenov~A.}
Finiteness properties for self-similar sets /
A.~Tetenov //
[Электронный ресурс] : URL: https://arxiv.org/abs/2003.04202v1

\bibitem{deltadef}
{\bf Drozdov D.}
On $\delta$-deformations of polygonal dendrites /
D.~Drozdov, M.~Samuel, A.~Tetenov //
[Электронный ресурс] : URL: https://arxiv.org/abs/1812.00439v1

\bibitem{TSV0}
{\bf Samuel~M.}
 Self-similar dendrites generated by polygonal systems in the plane /
 M.~Samuel, A.~Tetenov, D.~Vaulin // 
Sib. El. Math. Rep., № 14 (2017), C. 737 -- 751. 

% ссылки из адамовской статьи

\bibitem{ATK} Aseev, V. V.; Tetenov, A. V.; Kravchenko, A. S. Self-similar Jordan curves on
the plane.  Siberian Math. J. 44 (2003), no. 3, 379--386 MR1984698

\bibitem{BR}  {\bf Bandt, C.} Topology and separation of self-similar fractals in the plane / C. Bandt, H. Rao // Nonlinearity. -- 2007. -- vol.~20, no.~6. -- pp.~1463--1474.


\bibitem {C} Croydon~D., Random fractal dendrites, Ph.D. thesis, St. Cross College, University of Oxford, Trinity, 2006.


\bibitem{Kig95} Kigami~J., Harmonic calculus on limits of networks and its application to dendrites. J. Funct. Anal., 128(1):48-86, 1995.

% \bibitem{Kig}
% {  Kigami~J.}, Analysis on fractals. Cambridge Tracts in Mathematics
% 143, Cambridge University Press, 2001, 233 p.



\bibitem{TMV}
Tetenov A.~V., Mekhontsev D., Vauilin.~D: On weak separation property for plane dendrites. 	(to appear)

\bibitem{TSV0}
Samuel, M.; Tetenov, A.; Vaulin, D. Self-similar dendrites generated by polygonal systems in the plane. Sib. El. Math. Rep. 14 (2017), 737--751. MR3693741

\bibitem{TSV}
Tetenov A.~V., Samuel.~M, Mekhontsev D.:
On Dendrites Generated by Symmetric 
Polygonal Systems: The Case of Regular 
Polygons. in:  Trends in Mathematics, Advances in Algebra and Analysis: International Conference on Advances in Mathematical Sciences, Vellore, India, December 2017 - Volume I,  Springer, 2019, pp.17- 25.

\bibitem{TSM}
Tetenov A.~V., Samuel.~M, Vauilin.~D:
On dendrites generated by polyhedral systems and their ramification points.  Proc.  Krasovskii Inst. Math. Mech. UB RAS \textbf{23}(4), 281---291 (2017) DOI: 10.21538/0134-4889-2017-23-4-281-291


%\bibitem{MS}Samuel M.  On some problems in fractal geometry // Bharata Mata College Koch (Cochin Ernakulam), 2017

% ссылки про квадраты и кубы

\bibitem{bib:IFStile} 
    {\sc Mekhontsev D.,}
    {\em IFStile,} 
    {software, (2016-2024), \href{https://ifstile.com/}{URL:https://ifstile.com/}} 

\bibitem{bib:Olsen1998}    
    {\sc Olsen L.,}
    {\em Self-affine multifractal Sierpinski sponges in $\rr^d$,}
    {Pac. J. Math. \textbf{116} (1998), 143--199}

\bibitem{bib:EKM2010}    
    {\sc Elekes M., Keleti T., M\'ath\'e A.,}
    {\em Self-similar and self-affine sets: measure of the intersection of two copies,}
    {Ergod. Th. \& Dynam. Sys. \textbf{30} (2010), 399--440}


\end{thebibliography}