%\newpage
%
%
%\bibliographystyle {gost2008s}
%\bibliography {dissbib}
%\printbibliography
% \nocite {*} % добавляет непроцитированные источники из bib-файла


 \addcontentsline{toc}{chapter}{Список использованных источников и литературы} % Добавляем раздел в содержание

% \printbibliography[
%                     title = {Список использованных источников и литературы}]

\begin{thebibliography}{99}
% ссылки из магисерской
\bibitem{ATK}  
{\bf Асеев~В.~В.} 
О самоподобных жордановых кривых на плоскости / 
В.~В.~Асеев, А.~В~Тетенов., А.~С.~Кравченко //
Сиб. мат. журн., 2003, Т. 44, № 3, С.~481 -– 492.

\bibitem{2} 
{\bf Асеев~В.~В.} 
О жордановых самоподобных дугах, допускающих структурную параметризацию /
В.~В.~Асеев, А.~В.~Тетенов //
Сиб. матем. журн. (2005), том 46, № 4, С.~733 -– 748.

\bibitem{VDT} 
{\bf Ваулин Д.А.}
О связных компонетнах фрактальных кубов / 
Д.~А.~Ваулин, Д.~А.~Дроздов, А.~В.~Тетенов //
Труды ИММ УРО РАН, 2020, т.26, № 2, С.~98 -– 107.

\bibitem{TSV2017} 
{\bf Тетенов~А.~В.}  
О дендритах, заданных системами полиэдров и их точках ветвления /
А.~В.~Тетенов, М.~Самуэль, Д.~А.~Ваулин // 
Труды ИММ УРО РАН, 2017, т.23, № 4, С.~281 -– 291.

\bibitem{Tet06}
{\bf Тетенов~А.~В.}
Самоподобные жордановы дуги и граф-ориентированные системы подобий /
А.~В.~Тетенов //
Сиб. мат. журн. 2006. Т. 47, № 5, С.~1147 -– 1159.

\bibitem{Tet07}
{\bf Тетенов А.~В.} 
Структурные теоремы в теории самоподобных фракталов : диссертация на соискание уч. степени доктора физико-математических наук / А.В. Тетенов -- Горно-Алтайск, 2010. -- 216~с. 

\bibitem{Hata} 
{\bf Hata~M.}  
On the structure of self-similar sets /
M.~Hata //
Japan.~J.~Appl.~Math, № 3 (1985), С. 381 -- 414.

\bibitem{Kig}
{\bf Kigami~J.}, 
Analysis on fractals. Cambridge Tracts in Mathematics 143, 
Cambridge University Press, 2001, 233 p.

\bibitem{FPS}
{\bf Tetenov~A.}
Finiteness properties for self-similar sets /
A.~Tetenov //
[Электронный ресурс] : URL: https://arxiv.org/abs/2003.04202v1

\bibitem{deltadef}
{\bf Drozdov D.}
On $\delta$-deformations of polygonal dendrites /
D.~Drozdov, M.~Samuel, A.~Tetenov //
[Электронный ресурс] : URL: https://arxiv.org/abs/1812.00439v1

\bibitem{TSV0}
{\bf Samuel~M.}
 Self-similar dendrites generated by polygonal systems in the plane /
 M.~Samuel, A.~Tetenov, D.~Vaulin // 
Sib. El. Math. Rep., № 14 (2017), C. 737 -- 751. 

% ссылки из адамовской статьи

\bibitem{ATK} Aseev, V. V.; Tetenov, A. V.; Kravchenko, A. S. Self-similar Jordan curves on
the plane.  Siberian Math. J. 44 (2003), no. 3, 379--386 MR1984698

\bibitem{BR}  {\bf Bandt, C.} Topology and separation of self-similar fractals in the plane / C. Bandt, H. Rao // Nonlinearity. -- 2007. -- vol.~20, no.~6. -- pp.~1463--1474.

\bibitem{BS} Bandt, C., Stahnke, J.: Self-similar sets 6. Interior distance on deterministic fractals.
preprint, Greifswald 1990.

\bibitem{Char}
  Charatonik~J., Charatonik~W., Dendrites, Aportaciones Mat. Comun.
22 (1998), 227--253.

\bibitem{CS1} {Cristea~L.~L.}, {Steinsky~B.}, Curves of infinite length in $4 \times 4$-labyrinth fractals,{Geom. Dedicata}, 141(2009), 1--17.

\bibitem {CS2} {Cristea~L.~L.}, {Steinsky~B.},Curves of infinite length in labyrinth fractals, {Proc. Edinb. Math. Soc., II. Ser.}, 54(2011), no.2, 329--344.


\bibitem{CS3}  {Cristea~L.~L.}, {Steinsky~B.}, Mixed labyrinth fractals, {Topology Appl.}, 229(2017), 112--125.

\bibitem {C} Croydon~D., Random fractal dendrites, Ph.D. thesis, St. Cross College, University of Oxford, Trinity, 2006.

\bibitem{Hata}
Hata~M., On the structure of self-similar sets. Japan.J.Appl.Math 3(1985), 381-414.

\bibitem{Kig95} Kigami~J., Harmonic calculus on limits of networks and its application to dendrites. J. Funct. Anal., 128(1):48-86, 1995.

% \bibitem{Kig}
% {  Kigami~J.}, Analysis on fractals. Cambridge Tracts in Mathematics
% 143, Cambridge University Press, 2001, 233 p.

\bibitem{Kur}
Kuratowski~K.,  Topology, Volumes 1 and 2, Academic Press and PWN,
New York, 1966.

\bibitem{LLR} KA–SING LAU, JUN JASON LUO and HUI RAO (2013). Topological structure of fractal squares.
Mathematical Proceedings of the Cambridge Philosophical Society, 155, pp 73-86 doi:10.1017/S0305004112000692.

\bibitem{Str} {Strichartz~R.~S.}, Isoperimetric estimates on Sierpinski gasket type fractals, Trans. Amer.
Math. Soc. 351 (1999), pp.~1705.-1752

\bibitem{TF} {K.~Kamalutdinov, A.~Tetenov},  
Twofold Cantor sets in $\rr$ // Siberian Electr. Math. Rep., 15 (2018), pp. 801-814, DOI 10.17377/semi.2018.15.066.



\bibitem{TMV}
Tetenov A.~V., Mekhontsev D., Vauilin.~D: On weak separation property for plane dendrites. 	(to appear)

\bibitem{TSV0}
Samuel, M.; Tetenov, A.; Vaulin, D. Self-similar dendrites generated by polygonal systems in the plane. Sib. El. Math. Rep. 14 (2017), 737--751. MR3693741

\bibitem{TSV}
Tetenov A.~V., Samuel.~M, Mekhontsev D.:
On Dendrites Generated by Symmetric 
Polygonal Systems: The Case of Regular 
Polygons. in:  Trends in Mathematics, Advances in Algebra and Analysis: International Conference on Advances in Mathematical Sciences, Vellore, India, December 2017 - Volume I,  Springer, 2019, pp.17- 25.

\bibitem{TSM}
Tetenov A.~V., Samuel.~M, Vauilin.~D:
On dendrites generated by polyhedral systems and their ramification points.  Proc.  Krasovskii Inst. Math. Mech. UB RAS \textbf{23}(4), 281---291 (2017) DOI: 10.21538/0134-4889-2017-23-4-281-291


\bibitem{TSVa}
Tetenov A.~V., Samuel.~M, Vauilin.~D:
On dendrites generated by polyhedral systems and their ramification points.   www.arXiv.org/math.MG/1707.02875

% \bibitem{FPS}
% {\bf Tetenov~A.}
% Finiteness properties for self-similar sets //
%  https://arxiv.org/abs/2003.04202v1


%\bibitem{MS}Samuel M.  On some problems in fractal geometry // Bharata Mata College Koch (Cochin Ernakulam), 2017

% ссылки про квадраты и кубы

\bibitem{bib:IFStile} 
    {\sc Mekhontsev D.,}
    {\em IFStile,} 
    {software, (2016-2022), \href{https://ifstile.com/}{URL:https://ifstile.com/}} 

\bibitem{bib:FIP} 
    {\sc Tetenov A.,} 
    {\em Finiteness properties for self-similar sets,} (2021),
    \href{https://arxiv.org/abs/2003.04202}{arXiv:2003.04202} 

\bibitem{bib:peres1996}
    {\sc Kenyon R., Peres Y.,} 
    {\em Measures of full dimension on affine-invariant sets,}
    {Ergod. Th. \& Dynam. Sys. (2) \textbf{16} (1996), 307--323}

\bibitem{bib:peres1994}
    {\sc Peres Y.,}
    {\em The self-affine carpets of McMullen and Bedford have infinite Hausdorff measure,}
    {Math. Proc. Camb. Phil. Soc. (3) \textbf{116} (1994), 513--526}

\bibitem{bib:Hut1981}    
    {\sc Hutchinson J. E.,}
    {\em Fractals and self-similarity,}
    {Indiana Univ. Math. J. \textbf{30} (1981), 713--747}

\bibitem{bib:MW1988}    
    {\sc Mauldin R. D., Williams S. C.,}
    {\em Hausdorff dimension in graph directed constructions,}
    {Trans. Amer. Math. Soc. (2) \textbf{309} (1988), 811--829}

\bibitem{bib:Olsen1998}    
    {\sc Olsen L.,}
    {\em Self-affine multifractal Sierpinski sponges in $\rr^d$,}
    {Pac. J. Math. \textbf{116} (1998), 143--199}

\bibitem{bib:EKM2010}    
    {\sc Elekes M., Keleti T., M\'ath\'e A.,}
    {\em Self-similar and self-affine sets: measure of the intersection of two copies,}
    {Ergod. Th. \& Dynam. Sys. \textbf{30} (2010), 399--440}

\bibitem{bib:LLR2013}    
    {\sc Lau K., Luo J.J.,Rao H.}
    {\em Topological structure of fractal squares,}
    {Math. Proc. Camb. Phil. Soc. \textbf{155} (2013), 73--86}
    % добавить статьи про 5х5х5 и из БММ

\bibitem{Hut1981}
    {\sc Hutchinson J.},
    {\em Fractals and Self-Similarity},
    {Indiana University Mathematics Journal (5) \textbf{30} (1981), 713--747}

\end{thebibliography}